Network Configuration Synthesis with Abstract Topologies

### 2016-11-15 paper/abstraction/paper.tex
fix size

  \hrule
  \vspace*{1em}
  \caption{Abstract k-disjoint path analysis inference rules.}
  \label{fig:inference-rules}
  \vspace{-1.4em}
\end{figure*}

@@

  \vspace{1em}
  \noindent
  $\Con(\text{compile}(pol,G^A), \Gamma,f,G) = \text{compile}(\Con(pol,\Gamma,f),G)$
  \label{thm:concretization}
\end{thm}
%
\vspace{-.8em}
Full definitions of compilation and concretization, as well as the proof of Theorem~\ref{thm:concretization} are included in the appendix. These results also help assign semantics to templates.

@@

      Fattree~\cite{fattree} & -- & \cmark & \cmark & \cmark & \Conserv  \\ \hline
      Facebook~\cite{facebook-fattree} & -- & \cmark & \cmark & \cmark & \cmark \\ \hline
      F10~\cite{f10-fattree} & -- & \cmark & \cmark & \cmark & \Conserv \\ \hline
      VL2~\cite{vl2-fattree} & -- & \cmark & \cmark & \cmark & \Conserv \\ \hline
      BCube~\cite{bcube} & $k$ & \cmark & \cmark & \Conserv & \Conserv \\ \hline
      DCell~\cite{dcell} & $k$ & \cmark & \cmark & \Conserv & \Conserv \\ \hline
         %& HCN & $h$ & \cmark & \xmark \\
      Butterfly~\cite{butterfly} & $n$ & \cmark & \cmark & \cmark & \cmark \\ \hline
      Hypercube & $N$ & \cmark & \cmark & \cmark & \cmark \\ \hline
      HyperX~\cite{hyperx} & $L$ & \cmark & \cmark & \cmark & \cmark \\ \hline
      \end{tabular}
  \end{center}
  \vspace{-.6em}
  \caption{Expressiveness and precision of \sysname.}
  \label{fig:analysis-precision}
  \vspace{-1em}
\end{figure}

@@

  \caption{Example abstractions for HyperX and BCube.}
  \vspace*{-1em}%
  \label{fig:example-abstractions}
\end{figure}

@@

While we borrow much from existing configuration synthesis work, especially Propane~\cite{propane}, our goal is to generate role templates from abstract topologies, rather than router configurations from concrete topologies.
This goal aligns better with operators' mental models and tools and permits network evolution with minimal disruption to existing routers. In the process, we develop new abstractions for network topologies, compilation algorithms that generate templates, and analysis techniques that operate over classes of networks.

>>>>

  \hrule
  \vspace*{1em}
  \caption{Abstract k-disjoint path analysis inference rules.}
  \label{fig:inference-rules}
  \vspace{-.8em}
\end{figure*}

@@

  \vspace{1em}
  \noindent
  $\Con(\text{compile}(pol,G^A), \Gamma,f,G) = \text{compile}(\Con(pol,\Gamma,f),G)$
  \label{thm:concretization}
\end{thm}
%
\vspace{-.6em}
Full definitions of compilation and concretization, as well as the proof of Theorem~\ref{thm:concretization} are included in the appendix. These results also help assign semantics to templates.

@@

      Fattree~\cite{fattree} & -- & \cmark & \cmark & \cmark & \Conserv  \\ \hline
      Facebook~\cite{facebook-fattree} & -- & \cmark & \cmark & \cmark & \cmark \\ \hline
      F10~\cite{f10-fattree} & -- & \cmark & \cmark & \cmark & \Conserv \\ \hline
      VL2~\cite{vl2-fattree} & -- & \cmark & \cmark & \cmark & \Conserv \\ \hline
      BCube~\cite{bcube} & $k$ & \cmark & \cmark & \Conserv & \Conserv \\ \hline
      DCell~\cite{dcell} & $k$ & \cmark & \cmark & \Conserv & \Conserv \\ \hline
         %& HCN & $h$ & \cmark & \xmark \\
      Butterfly~\cite{butterfly} & $n$ & \cmark & \cmark & \cmark & \cmark \\ \hline
      Hypercube & $N$ & \cmark & \cmark & \cmark & \cmark \\ \hline
      HyperX~\cite{hyperx} & $L$ & \cmark & \cmark & \cmark & \cmark \\ \hline
      \end{tabular}
  \end{center}
  \vspace{-.6em}
  \caption{Expressiveness and precision of \sysname.}
  \label{fig:analysis-precision}
  %\vspace{-1em}
\end{figure}

@@

  \caption{Example abstractions for HyperX and BCube.}
  %\vspace*{-1em}%
  \label{fig:example-abstractions}
\end{figure}

@@

While we borrow much from existing configuration synthesis work, especially Propane~\cite{propane}, our goal is to generate role templates from abstract topologies, rather than router configurations from concrete topologies.
This goal aligns better with operators' mental models and tools and permits network evolution with minimal disruption. In the process, we develop new abstractions for network topologies, compilation algorithms that generate templates, and analysis techniques that operate over classes of networks.
